---
title: "Report of Adverse Food Events"
output: html_document
---
# Adverse Food Event 食物不良反應事件
source:https://www.kaggle.com/ambarish/detailed-eda-adverse-foodevents-w-advice/data

## Sort Data 
### (1)To read data
```{r message=FALSE, warning=FALSE}
library(tidyverse)
library(stringr)
library(lubridate)
library(DT)


rm(list=ls())

fillColor = "#FFA07A"
fillColor2 = "#F1C40F"

AdverseFoodEvents = read_csv("CAERS_ASCII_2004_2017Q2.csv")
```
###　(2)rename data
```{r}
AdverseFoodEvents = AdverseFoodEvents %>%
  rename(ReportNo = `RA_Report #`) %>%
  rename(CreatedDate = `RA_CAERS Created Date`) %>%
  rename(StartDate = `AEC_Event Start Date`) %>%
  rename(ProductRole = `PRI_Product Role`) %>%
  rename(ProductName = `PRI_Reported Brand/Product Name`) %>%
  rename(IndustryName = `PRI_FDA Industry Name`) %>%
  rename(AgeUnit = `CI_Age Unit`) %>%
  rename(AgeAtAdverseEvent = `CI_Age at Adverse Event`) %>%
  rename(Gender = `CI_Gender`) %>%
  rename(Outcomes = `AEC_One Row Outcomes`) %>%
  rename(Symptoms = `SYM_One Row Coded Symptoms`)

colnames(AdverseFoodEvents)
```

## Analyze
### (1) 10 Most Common Symptoms
For each report, there might be several symptoms recorded, so we need to use the "split()" function to remove "," . Then, find out the top ten symptoms and make a bar plot.
```{r}
BarPlotSymptoms = function(AdverseFoodEvents)
{
  Symptoms = str_split(AdverseFoodEvents$Symptoms,',') 

AllSymptoms <- data.frame(matrix(unlist(Symptoms),byrow=T),stringsAsFactors=FALSE)

colnames(AllSymptoms) = c("SymptomName")

#trimws returns a character string with leading and/or trailing whitespaces removed.
AllSymptoms$SymptomName = trimws(AllSymptoms$SymptomName)

AllSymptoms %>%
  group_by(SymptomName) %>%
  summarise(Count = n()) %>%
  arrange(desc(Count)) %>%
  ungroup() %>%
  mutate(SymptomName = reorder(SymptomName,Count)) %>%
  head(10) %>%
  
  ggplot(aes(x = SymptomName,y = Count)) +
  geom_bar(stat='identity',colour="white", fill = "skyblue") +
  geom_text(aes(x = SymptomName, y = 1, label = paste0("(",Count,")",sep="")),
            hjust=0, vjust=.5, size = 4, colour = 'black',
            fontface = 'bold') +
  labs(x = 'Symptom', 
       y = 'Count', 
       title = 'Symptom and Count') +
  coord_flip() + 
  theme_bw()
}

BarPlotSymptoms(AdverseFoodEvents)
```

## <font color="blue">* Result: Among adverse food events, the most common symptom is "Diarrhoea" <font>

### <font color="black">(2) 10 Most Common Product Name & Industry Name<font>
```{r}
par(mfrow = c(2,1)) 
AdverseFoodEvents %>%
  group_by(ProductName) %>%
  summarise(Count = n()) %>%
  arrange(desc(Count)) %>%
  ungroup() %>%
  mutate(ProductName = reorder(ProductName,Count)) %>%
  head(10) %>%
ggplot(aes(x = ProductName,y = Count)) +
  geom_bar(stat='identity',colour="white", fill = fillColor) +
  geom_text(aes(x = ProductName, y = 1, label = paste0("(",Count,")",sep="")),
            hjust=0, vjust=.5, size = 4, colour = 'black',
            fontface = 'bold') +
  labs(x = 'Product', 
       y = 'Count', 
       title = 'Product and Count') +
  coord_flip() + 
  theme_bw()
```
```{r}
AdverseFoodEvents %>%
  group_by(IndustryName) %>%
  summarise(Count = n()) %>%
  arrange(desc(Count)) %>%
  ungroup() %>%
  mutate(IndustryName = reorder(IndustryName,Count)) %>%
  head(10) %>%
ggplot(aes(x = IndustryName,y = Count)) +
  geom_bar(stat='identity',colour="white", fill = "orange") +
  geom_text(aes(x = IndustryName, y = 1, label = paste0("(",Count,")",sep="")),
            hjust=0, vjust=.5, size = 4, colour = 'black',
            fontface = 'bold') +
  labs(x = 'Industry', 
       y = 'Count', 
       title = 'Industry and Count') +
  coord_flip() + 
  theme_bw()
```

## <font color="blue">* Result: Compare the above two plots, it shows that "Vitamin Supplements" is the most common product causes adverse food events. Besides, other types of supplements and some cosmetics are the reason too.<front>

### <font color="black">(3) 各年齡層的事件發生率 <front>
Through the "if,else if" function, we can sort the data . As for "mutate()" function, it can add a new column  to replace the ole one (age). Then seperate the age as 10,20,30.....Last, make the plot.
```{r}
TransformIntoYears = function(ds)
{if(!is.na(ds["AgeAtAdverseEvent"]))
  { x = as.numeric(ds["AgeAtAdverseEvent"])
    ds["AgeAtAdverseEvent"] = as.numeric(ds["AgeAtAdverseEvent"])
    if(ds["AgeUnit"] == "Month(s)")
    {ds["AgeAtAdverseEventInYears"] = x/12}
    else if (ds["AgeUnit"] == "Weeks(s)")
    {ds["AgeAtAdverseEventInYears"] = x*7/365}
    else if (ds["AgeUnit"] == "Day(s)")
    {ds["AgeAtAdverseEventInYears"] = x*1/365}
    else if (ds["AgeUnit"] == "Decade(s)")
    {ds["AgeAtAdverseEventInYears"] = x*10}  }
    return(ds)}

AdverseFoodEvents = AdverseFoodEvents %>%
  mutate(AgeAtAdverseEventInYears = AgeAtAdverseEvent) 

AdverseFoodEvents$AgeAtAdverseEventInYears = 
  as.numeric(AdverseFoodEvents$AgeAtAdverseEventInYears)

AdverseFoodEvents = sapply(AdverseFoodEvents,TransformIntoYears)

AdverseFoodEvents = as.data.frame(AdverseFoodEvents)
breaks = c(10,20,30,40,50,60,70,80,90,100)

AdverseFoodEvents %>%
  filter(!is.na(AgeAtAdverseEventInYears)) %>%
  group_by(AgeAtAdverseEventInYears) %>%
  summarise(Count = n()) %>%
  ungroup() %>%
  mutate(AgeAtAdverseEventInYears = as.numeric(AgeAtAdverseEventInYears)) %>%
  
  ggplot(aes(x = AgeAtAdverseEventInYears,y = Count)) +
  geom_bar(stat='identity',colour="white", fill = "darkgreen") +
  scale_x_continuous(limits = c(0, 100),breaks=breaks ) +
  labs(x = 'Age in Years', 
       y = 'Count', 
       title = 'Age and Count') +
  
  theme_bw()
```

## <font color="blue">* Result: It seems that the elderly(around 60 to 85) are more likely to occur adverse food events *.<front>

### <font color="black">(4) 性別間的事件發生率 <front>
```{r}
AdverseFoodEvents %>%
  group_by(Gender) %>%
  filter(!is.na(Gender)) %>%
  summarise(Count = n()) %>%
  arrange(desc(Count)) %>%
  ungroup() %>%
  mutate(Gender = reorder(Gender,Count)) %>%
  head(10) %>%
  
  ggplot(aes(x = Gender,y = Count)) +
  geom_bar(stat='identity',colour="white", fill = "plum") +
  geom_text(aes(x = Gender, y = 1, label = paste0("(",Count,")",sep="")),
            hjust=0, vjust=.5, size = 4, colour = 'black',
            fontface = 'bold') +
  labs(x = 'Gender', 
       y = 'Count', 
       title = 'Gender and Count') +
  coord_flip() + 
  theme_bw()
```

## <font color="blue">* Result: Females report Adverse Events more than Males.<front>


# <font color="black">Conclusion:<front>
###<font color="blue">Most Likely to occur adverse food events<front>
####(1) The elderly 
####(2) Female
####(3) Use of vitamin supplement
###The Common symptoms are:
####1.Diahorrea
####2.Vomiting
####3.Nausea

